---
title: "prac3q10"
author: "E Poarch"
date: "2024-06-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the following you can see an example of how we can load pre-trained models in our codes.

```{r}
# Load the pre-trained MobileNet model

#run all code in source to load functions
mobilenet<-model_mobilenet_v2(pretrained = TRUE)

# Modify the last fully connected layer to match your classification task

#in_features <- mobilenet$classifier$in_features
mobilenet$classifier <- nn_linear(224*224*3, 2)   # Adjust the output size based on your classification task
mobilenet
```

```{r}
# Set the number of epochs
num_epochs <- 3

train_loss <- numeric(num_epochs)
train_acc <- numeric(num_epochs)
test_loss <- numeric(num_epochs)
test_acc <- numeric(num_epochs)

# Loop through the epochs
for (epoch in 1:num_epochs) {
  # Perform training and validation for each epoch
  mn.fitted <- mobilenet %>%
    setup(
      loss = nn_cross_entropy_loss(),
      optimizer = optim_adam,
      metrics = list(
        luz_metric_accuracy()
      )
    ) %>%
    fit(train_dataloader, epochs = 1, valid_data = test_dataloader)

  # Print the metrics for the current epoch
  cat("Epoch ", epoch, "/", num_epochs, "\n")
  cat("Train metrics: Loss: ", mn.fitted$records$metrics$train[[1]]$loss, " - Acc: ", mn.fitted$records$metrics$train[[1]]$acc, "\n")
  cat("Valid metrics: Loss: ", mn.fitted$records$metrics$valid[[1]]$loss, " - Acc: ", mn.fitted$records$metrics$valid[[1]]$acc, "\n")
  cat("\n")

  # Store the loss and accuracy values
  train_loss[epoch] <- mn.fitted$records$metrics$train[[1]]$loss
  train_acc[epoch] <- mn.fitted$records$metrics$train[[1]]$acc
  test_loss[epoch] <- mn.fitted$records$metrics$train[[1]]$loss
  test_acc[epoch] <- mn.fitted$records$metrics$valid[[1]]$acc
}
```

#Error in x$get_inherit() : attempt to apply non-function

**10_** Using the provided materials in this practical, train a different network architecture. Does this perform better?
  
#pre-processing tensors to N x 3 x 299 x 299 for inception model (https://rdrr.io/github/mlverse/torchvision/src/R/models-inception.R)
```{r}
process_images <- function(shuffled_dataset) {

  img_size <- 299  # Desired image size

  # Initialize an empty list to store processed images
  X <- list()

  # Loop through each image path in shuffled_train_dataset
  for (image_path in shuffled_dataset) {
    # Read the image
    img <- imager::load.image(image_path)

    # Normalize the image
    img_normalized <- img / 255

    # Resize the image
    img_resized <- resize(img_normalized, img_size, img_size)

    # Append the processed image to the list
    X <- c(X, list(img_resized))
  }

  return(X)
}
```

#encoding of labels
```{r, cache=TRUE}
train_X <- process_images(shuffled_train_dataset)
test_X <- process_images(shuffled_test_dataset)
val_X <- process_images(shuffled_val_dataset)

train_y <- ifelse(shuffled_train_labels == "normal", 1, 2)
test_y <- ifelse(shuffled_test_labels == "normal", 1, 2)
val_y <- ifelse(shuffled_val_labels == "normal", 1, 2)

train_y <- as.integer(train_y)
test_y <- as.integer(test_y)
val_y <- as.integer(val_y)
```

#visualize after processing.
```{r}
# Create a list to store the ggplot objects
plots <- list()

# Iterate through the images and labels
for (i in 1:4) {
  if (train_y[i] == 0) {
    label <- "Normal"
  } else {
    label <- "Pneumonia"
  }

  # Create a ggplot object for the image with the corresponding label
  plot <- ggplot() +
    theme_void() +
    ggtitle(label) +
    annotation_custom(
      rasterGrob(train_X[[i]], interpolate = TRUE),
      xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = Inf
    )

  # Add the ggplot object to the list
  plots[[i]] <- plot
}

# Arrange the plots in a 2x2 grid
grid.arrange(grobs = plots, nrow = 2, ncol = 2)
```

```{r}
train_X <- array(data = unlist(train_X), dim = c(1000, 299, 299, 3))
test_X <- array(data = unlist(test_X), dim = c(200, 299, 299, 3))
val_X <- array(data = unlist(val_X), dim = c(16, 299, 299, 3))
```

```{r}
#using the pre-trained model
inception<-model_inception_v3(pretrained = TRUE)

# Modify the last fully connected layer to match your classification task

#in_features <- mobilenet$classifier$in_features
inception$classifier <- nn_linear(299*299*3, 2)   # Adjust the output size based on your classification task
inception
```

```{r}
# Set the number of epochs
num_epochs <- 3

train_loss <- numeric(num_epochs)
train_acc <- numeric(num_epochs)
test_loss <- numeric(num_epochs)
test_acc <- numeric(num_epochs)

# Loop through the epochs
for (epoch in 1:num_epochs) {
  # Perform training and validation for each epoch
  in.fitted <- inception %>%
    setup(
      loss = nn_cross_entropy_loss(),
      optimizer = optim_adam,
      metrics = list(
        luz_metric_accuracy()
      )
    ) %>%
    fit(train_dataloader, epochs = 1, valid_data = test_dataloader)

  # Print the metrics for the current epoch
  cat("Epoch ", epoch, "/", num_epochs, "\n")
  cat("Train metrics: Loss: ", in.fitted$records$metrics$train[[1]]$loss, " - Acc: ", in.fitted$records$metrics$train[[1]]$acc, "\n")
  cat("Valid metrics: Loss: ", in.fitted$records$metrics$valid[[1]]$loss, " - Acc: ", in.fitted$records$metrics$valid[[1]]$acc, "\n")
  cat("\n")

  # Store the loss and accuracy values
  train_loss[epoch] <- in.fitted$records$metrics$train[[1]]$loss
  train_acc[epoch] <- in.fitted$records$metrics$train[[1]]$acc
  test_loss[epoch] <- in.fitted$records$metrics$train[[1]]$loss
  test_acc[epoch] <- in.fitted$records$metrics$valid[[1]]$acc
}
```

#Error in x$get_inherit() : attempt to apply non-function

